Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-04-05 fib2.tex
Fixed minor typos.

\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}

@@

\newcommand{\Eref}[1]{Eq.~(\ref{#1})}
\newcommand{\Fref}[1]{Fig.~\ref{#1}}
\newcommand{\Aref}[1]{Appendix~\ref{#1}}

@@

We consider encoding a qubit of quantum information in the global degeneracy associated 
with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this 
system of the form
\begin{align}
	H=-\sum_{i\in \Lambda}\proj{\mathbb{I}}_i\;,\label{e:hamiltonian}
\end{align}
with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground 
space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
conditions, this space is two-fold degenerate as noted above. We identify this ground space 
as the codespace of our model. Typical realistic noise processes in this kind of system are 
pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was 
seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
is sufficient to capture the qualitative features of an error-correction simulation, and so we 
will restrict to pair-creation noise processes in this study for convenience. These events act 
on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
uniformly at random at each timestep of the simulation. The simulation time, and thus the 
error-correction threshold, will be measured in terms of average number of noise processes 
per edge, as opposed to an iid noise probability per edge. The latter measure is not 
appropriate for error processes in nonabelian anyon models, but the two coincide in the limit 
of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).

@@

\begin{enumerate}[i)]
	\item The noise process is modelled by a sequence of pair-creation events distributed as 
	a Poisson process across each edge. Curves are created crossing the relevent edge 
	and terminating on the neighbouring sites.
	\item We first join curves that participate in the same tile in order to, 
	\cggb{maybe a couple more lines of detail on this and the next point?}
	\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
	\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
	is then measured (fused), and the decoder continues to cluster and fuse on larger 
	scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
	lattice. Since operators with support on such non-trivial clusters will generally perform an 
	undetectable error on the encoded state, in this case we abandon the simulation and 
	declare failure to error correct.
\end{enumerate}

>>>>

\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}

@@

\newcommand{\Eref}[1]{Eq.~(\ref{#1})}
\newcommand{\Fref}[1]{Fig.~\ref{#1}}

@@

We consider encoding a qubit of quantum information in the global degeneracy associated 
with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this 
system of the form
\begin{align}
	H=-\sum_{i\in \Lambda}\proj{\mathbb{I}}_i\;,\label{e:hamiltonian}
\end{align}
with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground 
space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
conditions, this space is two-fold degenerate as noted above. We identify this ground space 
as the codespace of our model. Typical realistic noise processes in this kind of system are 
pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was 
seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
is sufficient to capture the qualitative features of an error-correction simulation, and so we 
will restrict to pair-creation noise processes in this study for convenience. These events act 
on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
uniformly at random at each time step of the simulation. The simulation time, and thus the 
error-correction threshold, will be measured in terms of average number of noise processes 
per edge, as opposed to an iid noise probability per edge. The latter measure is not 
appropriate for error processes in nonabelian anyon models, but the two coincide in the limit 
of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).

@@

\begin{enumerate}[i)]
	\item The noise process is modelled by a sequence of pair-creation events distributed as 
	a Poisson process across each edge. Curves are created crossing the relevant edge 
	and terminating on the neighbouring sites.
	\item We first join curves that participate in the same tile in order to, 
	\cggb{maybe a couple more lines of detail on this and the next point?}
	\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
	\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
	is then measured (fused), and the decoder continues to cluster and fuse on larger 
	scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
	lattice. Since operators with support on such non-trivial clusters will generally perform an 
	undetectable error on the encoded state, in this case we abandon the simulation and 
	declare failure to error correct.
\end{enumerate}
